### 2019-07-27 monograph/thesis/chapters/beautifiers.tex
Moved Obfuscators section under Source Code Formatters section
Fixed URLs being used instead of direct citation

\lang{%
    The problem about is,
    even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case,
    C, C++, Java, Pawn,
    etc.
    For all other languages you still need to find out another source code formatter tool,
    which will be certainly limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}} and
    still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.

@@

@@

Ofuscadores\footnote{Do inglês,
\textit{Obfuscator}, \url{https://en.wikipedia.org/wiki/Obfuscation_(software)}
}
são formatadores de código que funcionam com objetivo contrário,
veja o Quadro \ref{exemploDeOfuscador}.
Em vez de melhorar a leitura do código~=fonte,
sua função é impossibilitar que o código~=fonte seja compreendido.
Tais técnicas e
utilidades para estes tipos de software podem ser encontradas em \citeonline{codeObfuscationTechniques}.

>>>>

\lang{%
    The problem about is,
    even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case,
    C, C++, Java, Pawn,
    etc.
    For all other languages you still need to find out another source code formatter tool,
    which will be certainly limited \cite{eclisePeriodSettings} and
    still need to configure all over again.
}{%
    O problema é,
    mesmo que se passe por todas essas configurações,
    realizando os ajustes de preferência do usuário,
    isso levará um bom tempo.
    Infelizmente,
    você ainda está apenas configurando uma e
    talvez algumas linguagens fortemente relacionadas,
    dependendo do suporte que a ferramenta oferece.

@@

Ofuscadores\footnote{Do inglês,
\textit{Obfuscator},
\citetitle{obfuscationWikipedia}.
}
são formatadores de código que funcionam com objetivo contrário,
veja o Quadro \ref{exemploDeOfuscador}.
Em vez de melhorar a leitura do código~=fonte,
sua função é impossibilitar que o código~=fonte seja compreendido.
Tais técnicas e
utilidades para estes tipos de software podem ser encontradas em \citeonline{codeObfuscationTechniques}.

@@
